---
title: "Diagram for the 1st Approach - deworming"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DiagrammeR)
```

Diagram

```{r echo=FALSE}
add_mathjax(
  grViz(
"
digraph relationship {

# node definitions with substituted label text
# First level
node [fontname = Helvetica, shape = box]
NPV [label = '$NPV (1) $']## label indicates the position of the letter

# Second level
node [fontname = Helvetica, shape = box, fontsize = 10, fixedsize = TRUE]
B [label = '$B (2)$']
C [label = '$C (10)$']

# Third level
node [fontname = Helvetica, shape = box, fixedsize = TRUE]
r [label = '$r (3)$']
Et [label = '$E_t (4)$']
DC [label = '$DC (11)$']
IC [label = '$IC$']

# Fourth level
node [fontname = Helvetica, shape = box, fixedsize = TRUE]
g [label = '$g$']
pi [label = '$\\\\pi$']
wt [label = '$w_t (5)$']
lambda1 [label = '$\\\\lambda_1 (8)$']
lambda2 [label = '$\\\\lambda_2$']
p [label = '$p (9)$']
R [label = '$R$']

S1 [label = '$S_1$']
QS1 [label = '$Q(S_1)$']
S2 [label = '$S_2$']
QS2 [label = '$Q(S_2)$']

K [label = '$K$']

node [fontname = Helvetica, shape = box, fixedsize = FALSE]
DeltaEt [label = '$\\\\Delta\\\\bar{E_t}(S_1, S_2)$']

# Fifth Level
node [fontname = Helvetica, shape = box, fixedsize = TRUE]
w0 [label = '$w_0$']
Xp [label = '$X_p$']
beta1 [label = '$\\\\hat{\\\\beta_1}$']
beta2 [label = '$\\\\hat{\\\\beta_2}$']
lambda1m [label = '$\\\\lambda_{1, male}$']
lambda1f [label = '$\\\\lambda_{1, female}$']
R [label = '$R$']
Qfull [label = '$Q(full)$']
Q0 [label = '$Q(0)$']

KSH [label = '$KSH$']
ex [label = '$ex$']
t [label = '$t$']

# 6th level
wl [label = '$w_l$']
alphal [label = '$\\\\alpha_l$']

# 7th level
hl [label = '$h_l$']
hag [label = '$h_{ag}$']
hww [label = '$h_{ww}$']
hse [label = '$h_{se}$']

# edge definitions with the node IDs
NPV -> {B C}       ##[label = ...] adds text on the edge
B -> {r Et} 
C -> {DC IC} 
r -> {g pi} 
Et -> {wt lambda1 lambda2 p R} 
DC -> {S1 QS1 S2 QS2} 
IC -> {K r DeltaEt}
wt -> {w0 g Xp beta1 beta2}
lambda1 -> {lambda1m lambda1f}
p -> {R Qfull Q0}
S2 -> {KSH ex t}
w0 -> {wl alphal}
alphal -> {hl hag hww hse}
}
")
)
```
## Notations

### First level
- $NPV$: Net Present Value

### Second level
- $B$: Benefit
- $C$: Cost

### Third level
- $E_t$: Effect on earnings
- $DC$: Direct deworming costs
- $IC$: Indirect deworming costs

### 4th level
- $\lambda_1$: direct effects of deworming on earnings
- $\lambda_2$: indirect effects of deworming on earnings
- $p$: saturation, measures the fraction of the population that is effectively using the treatment
- $w_t$: earnings in period t
- $r$: real interest rate
- $S_1$: take-up under a no deworming intervention
- $Q(S_1)$: the per-capita costs of deworming under no government intervention
- $S_2$: take-up under a mass deworming intervention
- $Q(S_2)$: the per-capita costs of deworming under the intervention
- $\Delta\bar{E_t}(S_1, S_2)$: the estimated increase in school attendance
- $K$: cost per student

### 5th level
- $\lambda_{1, male}$: the estimated impact of deworming on hours of work for men
- $\lambda_{1, female}$: the estimated impact of deworming on hours of work for women
- $R$: coverage, defined as the fraction, among all neighboring schools (within 6 km), that belongs to the treatment group. (note: $R = 0.68$)
- $Q(full)$: the estimated take-up with full subsidy ($Q(full) = 0.75$)
- $Q(0)$: the value of 0, because there is almost no take-up without subsidy for this (or similar?) setting (*Miguel and Kremer 2007)
- $w_0$: The initial wage in dollars
- $X_p$: years of work
- $\hat{\beta}_1$: the estimated coefficient for years of work
- $\hat{\beta}_2$: the estimated coefficient for squared years of work
- $g$: interest rate on goverment bonds ($g = 0.118$)
- $\pi$: the inflation rate ($\pi = 0.02$)
- $t$: additional years of treatment
- $KSH$: Cost per person per year
- $ex$: ???

### 6th level:
- $w_l$: wages in agriculture, working wage, and self-employed sectors
- $\alpha_l$: weights for each of the above sectors

### 7th level:
- $h_l$: the average number of hours in each sector
- $h_{ag}$: wages for control group in agriculture
- $h_{ww}$: wages for control group in working wage
- $h_{se}$: wages for control group in self-employed sectors

