---
title: "Diagram for the 2nd Approach - deworming"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DiagrammeR)
```

Diagram

```{r echo=FALSE}
add_mathjax(
  grViz(
"
digraph relationship {

# node definitions with substituted label text
# First level
node [fontname = Helvetica, shape = box]
NPV [label = '$NPV (1) $']## label indicates the position of the letter

# Second level
node [fontname = Helvetica, shape = box, fontsize = 10, fixedsize = TRUE]
B [label = '$B (2)$']
C [label = '$C (10)$']

# Third level
node [fontname = Helvetica, shape = box, fixedsize = TRUE]
r [label = '$r (3)$']
Et [label = '$E_t (4)$']
DC [label = '$DC (11)$']
IC [label = '$IC$']

# Fourth level
node [fontname = Helvetica, shape = box, fixedsize = TRUE]
g [label = '$g$']
pi [label = '$\\\\pi$']

alphaKLPS2 [label = '$\\\\alpha^{KLPS2}$']
alphaKLPS3 [label = '$\\\\alpha^{KLPS3}$']
alphaKLPS4 [label = '$\\\\alpha^{KLPS4}$']
 
S1 [label = '$S_1$']
QS1 [label = '$Q(S_1)$']
S2 [label = '$S_2$']
QS2 [label = '$Q(S_2)$']

K [label = '$K$']

node [fontname = Helvetica, shape = box, fixedsize = FALSE]
DeltaEt [label = '$\\\\Delta\\\\bar{E_t}(S_1, S_2)$']

KSH [label = '$KSH$']
ex [label = '$ex$']
t [label = '$t$']

# edge definitions with the node IDs
NPV -> {B C}       ##[label = ...] adds text on the edge
B -> {r Et} 
C -> {DC IC} 
r -> {g pi} 
Et -> {alphaKLPS2 alphaKLPS3 alphaKLPS4} 
DC -> {r t S1 QS1 S2 QS2} 
IC -> {K r DeltaEt t}
S2 -> {KSH ex t}
}
")
)
```
## Notations

### First level
- $NPV$: Net Present Value

### Second level
- $B$: Benefit
- $C$: Cost

### Third level
- $E_t$: Effect on earnings
- $DC$: Direct deworming costs
- $IC$: Indirect deworming costs

### 4th level
- $\alpha^{KLPS2}$: welfare gains from deworming after 10 years
- $\alpha^{KLPS3}$: welfare gains from deworming after 15 years
- $\alpha^{KLPS4}$: welfare gains from deworming after 20 years
- $\Delta\bar{E_t}(S_1, S_2)$: the estimated increase in school attendance
- $K$: cost per student
- $S_1$: take-up under a no deworming intervention
- $Q(S_1)$: the per-capita costs of deworming under no government intervention
- $S_2$: take-up under a mass deworming intervention
- $Q(S_2)$: the per-capita costs of deworming under the intervention


### 5th level
- $g$: interest rate on goverment bonds ($g = 0.118$)
- $\pi$: the inflation rate ($\pi = 0.02$)
- $t$: additional years of treatment
- $KSH$: Cost per person per year
- $ex$: ???


