---
title: "Diagram for the 2nd Approach - deworming"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DiagrammeR)
```

Diagram

```{r echo=FALSE}
add_mathjax(
  grViz(
"
digraph relationship {

# node definitions with substituted label text
# First level
node [fontname = Helvetica, shape = box]
CEA [label = '$CEA_{deworming} (21)$']

# Second level
node [fontname = Helvetica, shape = box, fontsize = 10, fixedsize = TRUE]
B [label = '$B (2)$']
C [label = '$C$']
F0 [label = '$F_0$']

# Third level
node [fontname = Helvetica, shape = box, fixedsize = TRUE]
r [label = '$r (3)$']
Et [label = '$E_t (4)$']
wi [label = '$w_i (19)$']
ci [label = '$c_i$']

# Fourth level
node [fontname = Helvetica, shape = box, fixedsize = TRUE]
g [label = '$g$']
pi [label = '$\\\\pi$']

Ni [label = '$N_i$']
Nj [label = '$N_j$']
Ci [label = '$C_i$']

wt [label = '$w_t (5)$']
lambda1 [label = '$\\\\lambda_1 (20)$']
lambda2 [label = '$\\\\lambda_2$']
p [label = '$p (9)$']
R [label = '$R$']

# 5th level
deltag [label = '$\\\\delta_{g}$']
Cik [label = '$C_{i,k}$']
w0 [label = '$w_0$']
Xp [label = '$X_p$']
beta1 [label = '$\\\\hat{\\\\beta_1}$']
beta2 [label = '$\\\\hat{\\\\beta_2}$']
lambda1eff [label = '$\\\\lambda_1^{eff}$'] 
alpha [label = '$\\\\alpha$'] 
R [label = '$R$']
Qfull [label = '$Q(full)$']
Q0 [label = '$Q(0)$']

# 6th level
Ciklm [label = '$C_{i,k,l,m}$']

# edge definitions with the node IDs
CEA -> {B C F0}       ##[label = ...] adds text on the edge
B -> {r Et} 
C -> {wi ci} 
r -> {g pi} 
Et -> {wt lambda1 lambda2 p R}
wt -> {w0 g Xp beta1 beta2}
lambda1 -> {lambda1eff alpha}
p -> {R Qfull Q0}
wi -> {Ni Nj}
ci -> {Ni Ci}
Ci -> {deltag Cik}
Cik -> {Ciklm}
}
")
)
```
## Notations

### First level
- $CEA_{deworming}$: cost effectiveness ratio for deworming

### Second level
- $B$: Benefits per person dewormed
- $C$: Cost per person dewormed
- $F_0$: a factor to account for leverage/fudging (not reviewed in this excercise)

### Third level
- $E_t$: Effect on earnings
- $w_i$: Weight for the weighted average
- $c_i$: Total cost per child, per year in country i

### 4th level
- $g$: interest rate on goverment bonds ($g = 0.118$)
- $\pi$: the inflation rate ($\pi = 0.02$)
- $N_j$: Number of treated children in country j
- $N_i$: Number of treated children in country i
- $C_i$: Costs in country i

### 5th level
- $C_{i,k}$: Costs in country i distributed across k payers.
- $C_{i,k,l,m}$: ???
- $\delta_g$: depreciation???
- $\alpha$: the incidence of the condition.
- $\lambda_1^{eff}$: the effect of deworming over those affected with the condition.

k: Costs distribute across k payers.
l: Each payers costs come from l items.

